---
title: "SingularityNET Ecosystem Analysis"
date: "Last updated: `r Sys.Date()`"
output: html_notebook
---

## Preliminary Work: Install/Load Packages

To try and ensure that this R Notebook will run successfully, we'll use the [renv package](https://cran.r-project.org/web/packages/renv/index.html) to create a project-specific library of packages. This will allow us to install the packages that we need for this project without affecting any other projects that we may be working on. Additionally, the project library will track the specific versions of the dependency packages so that any updates to those packages will not break this project.

The code chunk below will first install the renv package if it is not already installed. Then we will load the package. Next, we'll use the `restore()` function to install any packages listed in the renv.lock file. Once these packages are installed, we can load them into the R session using the `library()` commands. Below the code chunk, we'll list out the packages that will be used in the project demo. And if you run into any trouble using renv, then you can use the second code chunk below and that should be an even more reliable approach to install the required packages.

```{r setup, results='hide', message=FALSE}
# Install renv package if not already installed
if(!"renv" %in% installed.packages()[,"Package"]) install.packages("renv")
# Load renv package
library(renv)
# Use restore() to install any packages listed in the renv.lock file
renv::restore(clean=TRUE, lockfile="../renv.lock")
# Load in the packages
library(geckor)
library(dplyr)
library(xts)
library(ggplot2)
```

* The [geckor package](https://github.com/next-game-solutions/geckor) is a wrapper for the [CoinGecko API](https://www.coingecko.com/en/api) and allows for easy import of bitcoin price data.
* The [dplyr package](https://cran.r-project.org/package=dplyr) package enables additional functionality for transforming data frames.
* The [xts package](https://cran.r-project.org/package=xts) is short for 'eXtensible Time Series', which contains tools for working with time series data.
* The [ggplot2 package](https://cran.r-project.org/package=ggplot2) for graphics and visuals.

Since the rmarkdown functionality is built into RStudio, this one is automatically loaded when we open the RStudio. So no need to use the `library()` function for this one. Another observation to make about the code chunk above is that it is labeled as 'setup', which is a special name, which the R Notebook will recognize and automatically run prior to running any other code chunk. This is useful for loading in packages and setting up other global options that will be used throughout the notebook. 

Then if you wish to try and update the versions of the various R packages in the lock file, you can use the `renv::update()` function to update the packages in the project library. However, it is possible that these updates could break the code in this notebook. If so, you may need to adapt the code to work with the updated packages.

My recommendation is to first run through the code using the versions of the packages in the lock file. Then if you want to try and update the packages, you can do so and then run through the code again to see if it still works. If not, you can always revert back to the lock file versions using the `renv::restore()` function.

If you update the packages and get everything working successfully, then you can update the lock file using the `renv::snapshot()` function. This will update the lock file with the versions of the packages that are currently installed in the project library. Then you can commit the updated lock file to the repository so that others can use the updated versions of the packages.

### Alternative Package Installation Code

If you run into any trouble using renv in the code chunk above, then you can use the code chunk below to install the required packages for this analysis. This method will first check if you have already installed the packages. If any are missing, it will then install them. Then it will load the packages into the R session. A potential flaw in this approach compared to using renv is that it will simply install the latest versions of the packages, which could potentially break some of the code in this notebook if any of the updates aren't backwards compatible. 

As long as you have downloaded the entire project repository, the renv chunk above will likely be managing the packages. Thus, the `eval=FALSE` option is used to prevent this chunk from running unless manually executed. So if you only downloaded this one Rmd file, this code chunk should take care of installing the packages for you.

```{r setup2, results='hide', message=FALSE, eval=FALSE}
# Create list of packages needed for this exercise, omit geckor since its not on CRAN
list.of.packages = c("devtools","dplyr","xts","ggplot2","rmarkdown")
# Check if any have not yet been installed
new.packages = list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
# If any need to be installed, install them
if(length(new.packages)) install.packages(new.packages)
# Since geckor is no longer published to CRAN, install via GitHub
library(devtools)
devtools::install_github("next-game-solutions/geckor")
# Load in the remaining packages
library(geckor)
library(dplyr)
library(xts)
library(ggplot2)
```


## Price Data Import

Before we use the geckor package to import price data for the various crypto tokens, we need to create a vector of character strings that correspond to the CoinGecko ids for the coins/tokens that we'd like to analyze. These can be found by manually going to an asset's page on [CoinGecko.com](https://www.coingecko.com/) and copying the "API id" from the Info section. These ids also appear in the page url as well. 

Once we have this list of coins, we can use the `coin_history_range()` function to download the daily price data in USD. The API requires that the start and end date parameters for the request are provided in a [POSIXct  date format](https://search.brave.com/search?q=POSIXct). This is done with the `as.POSIXct()` function. For a starting point, we'll use the first date that CoinGecko has an observed market capitalization for the original SingularityNET token (AGIX), which is February 1, 2018. The `Sys.Date()` function returns the current date, which is used as the end date for the request so that we pull as much data as possible.

Currently, the free CoinGecko API has restrictions on both the number of assets per request and the overall usage (call credits/min). The limit on the number of coins per request is 5. So for the 8 assets of this analysis, we must split this into two requests to get all the price data. The two responses are then combined into a single data frame using `rbind()`.

```{r pricedata}
coinids = c("ethereum","singularitynet","singularitydao","nunet","rejuve-ai","hypercycle","cogito-protocol","sophiaverse")
prices1 = coin_history_range(coin_id=coinids[1:4],
                            vs_currency = "usd",
                            from = as.POSIXct("2018-02-01"),
                            to = as.POSIXct(Sys.Date()))
# Pause for 120 seconds to avoid API rate limit
Sys.sleep(120)
prices2 = coin_history_range(coin_id=coinids[5:8],
                            vs_currency = "usd",
                            from = as.POSIXct("2023-03-16"), # RJV beginning
                            to = as.POSIXct(Sys.Date()))
prices = rbind(prices1,prices2)
```


## Data Cleaning

Reformat each of the variables to an appropriate data type. The `timestamp` variable is converted to a date format, since the extra time elements of the POSIXct data type are not needed. The `coin_id` variable is reformatted to the factor data type since there are just a small number of categories. Then the `vs_currency` variable is deleted since all the prices are in USD units. Lastly, the `price`, `total_volume`, and `market_cap` variables are already in numeric formats, so nothing needs to be done for those.

```{r cleanformats}
prices_clean1 = prices
prices_clean1$timestamp = as.Date(prices_clean1$timestamp)
prices_clean1$coin_id = as.factor(prices_clean1$coin_id)
prices_clean1$vs_currency = NULL
```

The next data cleaning step is to resolve a missing observation in the price series for the AGIX token on June 6, 2021. The next chunk will impute this missing observation by taking the average of the previous and next day's market cap, volume, and price. 

```{r fixmissing}
imputedobs = data.frame(timestamp=as.Date("2021-06-06"),
                        coin_id="singularitynet",
                        # Use the average of the previous and next day's price
                        price=mean(prices_clean1$price[prices$coin_id=="singularitynet" & prices$timestamp %in% as.Date(c("2021-06-05","2021-06-07"))]),
                        # Use the average of the previous and next day's trading volume
                        total_volume=mean(prices_clean1$total_volume[prices$coin_id=="singularitynet" & prices$timestamp %in% as.Date(c("2021-06-05","2021-06-07"))]),
                        # Use the average of the previous and next day's market cap
                        market_cap=mean(prices_clean1$market_cap[prices$coin_id=="singularitynet" & prices$timestamp %in% as.Date(c("2021-06-05","2021-06-07"))]))
# Insert imputed observation into data frame in appropriate position
prevobs = max(which(prices_clean1$coin_id=="singularitynet" & prices_clean1$timestamp==as.Date("2021-06-05")))
prices_clean2 = rbind(prices_clean1[1:prevobs,],
                      imputedobs,
                      prices_clean1[(prevobs+1):nrow(prices_clean1),])
```

Then before we get into the rest of the data cleaning process, let's create a new asset that represents the aggregate market capitalization of all the SingularityNET ecosystem tokens. This will be useful for comparing the growth of the ecosystem to the growth of the individual projects. We can do this by summing the market caps of each of the tokens. 

```{r snet}
snet = prices_clean2 |>
  filter(coin_id %in% c("singularitynet","singularitydao","nunet","rejuve-ai","hypercycle","cogito-protocol","sophiaverse")) |>
  group_by(timestamp) |>
  summarise(market_cap=sum(market_cap),
            total_volume=sum(total_volume))
snet$coin_id = "snet-ecosystem"
snet$price = snet$market_cap
prices_clean3 = rbind(prices_clean2,snet)
coinids_clean = c(coinids,"snet-ecosystem")
```

The following code chunk is a large one. This is because we loop the cleaning for each coin/token. So be sure to read the comments within the code chunk for more explanation of the steps in the process. After isolating the observations for a coin, it creates a separate xts object for three different frequencies of analysis: daily, weekly, and monthly. The less frequent series have a cost in that there are fewer observations to study. However, as time moves on, we will have more data to analyze. Then for each of those frequencies, we calculate the annualized returns, annualized growth rates in market cap, and daily growth rates in trading volume.

```{r cleanloop}
dfs_daily = list()
dfs_weeks = list()
dfs_month = list()

#coin = coinids[1]
for (coin in coinids_clean) {
  # Start timer
  t = proc.time()
  # Extract price data for each coin
  subdf = filter(prices_clean3, coin_id==coin)
  # Create xts object for each frequency
  dailyxts = xts(subdf[,3:5], order.by=as.Date(subdf$timestamp))
  weeksxts = to.weekly(dailyxts)
  monthxts = to.monthly(dailyxts)
  # Calculate annualized return of the coin's price movements
  dailyxts$annret = (log(as.numeric(dailyxts$price)) - log(as.numeric(lag(dailyxts$price))))*365*100
  weeksxts$annret = (log(as.numeric(weeksxts$dailyxts.Close)) - log(as.numeric(lag(weeksxts$dailyxts.Close))))*(365/7)*100
  monthxts$annret = (log(as.numeric(monthxts$dailyxts.Close)) - log(as.numeric(lag(monthxts$dailyxts.Close))))*12*100
  # Calculate alternative annualized return measurement from the market cap of the coin
  dailyxts$annret2 = (log(as.numeric(dailyxts$market_cap)) - log(as.numeric(lag(dailyxts$market_cap))))*365*100
    # Since to.weekly and to.monthly only convert prices by default, we must run again for market caps.
  weeksxts2 = to.weekly(dailyxts$market_cap)
  weeksxts$annret2 = (log(as.numeric(weeksxts2$`dailyxts$market_cap.Close`)) - log(as.numeric(lag(weeksxts2$`dailyxts$market_cap.Close`))))*(365/7)*100
  monthxts2 = to.monthly(dailyxts$market_cap)
  monthxts$annret2 = (log(as.numeric(monthxts2$`dailyxts$market_cap.Close`)) - log(as.numeric(lag(monthxts2$`dailyxts$market_cap.Close`))))*12*100
  # Also calculate volume growth rates and reduce to daily values
  dailyxts$volgrowth = (log(as.numeric(dailyxts$total_volume)) - log(as.numeric(lag(dailyxts$total_volume))))*100
  weeksxts$volgrowth = (log(as.numeric(weeksxts$dailyxts.Volume)) - log(as.numeric(lag(weeksxts$dailyxts.Volume))))*100/7
  monthxts$volgrowth = (log(as.numeric(monthxts$dailyxts.Volume)) - log(as.numeric(lag(monthxts$dailyxts.Volume))))*100/(365/12)
  # Save data frames to output object
  dfs_daily[[coin]] = dailyxts
  dfs_weeks[[coin]] = weeksxts
  dfs_month[[coin]] = monthxts
  # Stop timer and output result
  T = proc.time() - t
  print(paste("Cleaning of", coin, "completed in", as.character(round(T[3],2)), "seconds."))
}
```


## Multivariate Return Distributions

Compute the average annual return and volatility of each of the coins/tokens, as well as the correlation matrix, for the daily return series.

```{r dailycors}
# Compile data frame of annualized (price) returns
daily_annrets = merge(dfs_daily$ethereum$annret,
                      dfs_daily$singularitynet$annret,
                      dfs_daily$singularitydao$annret,
                      dfs_daily$nunet$annret,
                      dfs_daily$`rejuve-ai`$annret,
                      dfs_daily$hypercycle$annret,
                      dfs_daily$`cogito-protocol`$annret,
                      dfs_daily$sophiaverse$annret,
                      dfs_daily$`snet-ecosystem`$annret)
# Correct variable names
colnames(daily_annrets) = c("ETH", "AGIX", "SDAO", "NTX", "RJV", "HYPC", "CGV", "SOPH", "SNET")
# Compute average annual returns, volatility, and correlations
Er_daily = colMeans(daily_annrets,na.rm=TRUE)
Er_daily |> round(2)
sd_daily = apply(daily_annrets,2,sd,na.rm=TRUE)
sd_daily |> round(2)
Sharpe_daily = Er_daily/sd_daily
Sharpe_daily |> round(2)
cor(daily_annrets, use="pairwise.complete.obs") |> round(2)
```

Compute the average annual return and volatility of each of the coins/tokens, as well as the correlation matrix, for the weekly return series.

```{r weeklycors}
# Compile data frame of annualized (price) returns
weeks_annrets = merge(dfs_weeks$ethereum$annret,
                      dfs_weeks$singularitynet$annret,
                      dfs_weeks$singularitydao$annret,
                      dfs_weeks$nunet$annret,
                      dfs_weeks$`rejuve-ai`$annret,
                      dfs_weeks$hypercycle$annret,
                      dfs_weeks$`cogito-protocol`$annret,
                      dfs_weeks$sophiaverse$annret,
                      dfs_weeks$`snet-ecosystem`$annret)
# Correct variable names
colnames(weeks_annrets) = c("ETH", "AGIX", "SDAO", "NTX", "RJV", "HYPC", "CGV", "SOPH", "SNET")
# Compute average annual returns, volatility, and correlations
Er_weeks = colMeans(weeks_annrets,na.rm=TRUE)
Er_weeks |> round(2)
sd_weeks = apply(weeks_annrets,2,sd,na.rm=TRUE)
sd_weeks |> round(2)
Sharpe_weeks = Er_weeks/sd_weeks
Sharpe_weeks |> round(2)
cor(weeks_annrets, use="pairwise.complete.obs") |> round(2)
```

Compute the average annual return and volatility of each of the coins/tokens, as well as the correlation matrix, for the monthly return series.

```{r monthlycors}
# Compile data frame of annualized (price) returns
month_annrets = merge(dfs_month$ethereum$annret,
                      dfs_month$singularitynet$annret,
                      dfs_month$singularitydao$annret,
                      dfs_month$nunet$annret,
                      dfs_month$`rejuve-ai`$annret,
                      dfs_month$hypercycle$annret,
                      dfs_month$`cogito-protocol`$annret,
                      dfs_month$sophiaverse$annret,
                      dfs_month$`snet-ecosystem`$annret)
# Correct variable names
colnames(month_annrets) = c("ETH", "AGIX", "SDAO", "NTX", "RJV", "HYPC", "CGV", "SOPH", "SNET")
# Compute average annual returns, volatility, and correlations
Er_month = colMeans(month_annrets,na.rm=TRUE)
Er_month |> round(2)
sd_month = apply(month_annrets,2,sd,na.rm=TRUE)
sd_month |> round(2)
Sharpe_month = Er_month/sd_month
Sharpe_month |> round(2)
cor(month_annrets, use="pairwise.complete.obs") |> round(2)
```

## ETH-adjusted Returns

Now let's examine the relationship of the returns on the SingularityNET tokens to that of Ethereum, which is the blockchain that the tokens primarily transact on.

First up is the SingularityNET token (AGIX):

```{r agixregs}
AGIXfit_daily = lm(AGIX~ETH, data=daily_annrets)
summary(AGIXfit_daily)
ggplot(daily_annrets,aes(y=AGIX, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
daily_annrets$AGIXresid = xts(resid(AGIXfit_daily), order.by=as.Date(names(resid(AGIXfit_daily))))

AGIXfit_weeks = lm(AGIX~ETH, data=weeks_annrets)
summary(AGIXfit_weeks)
ggplot(weeks_annrets,aes(y=AGIX, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
weeks_annrets$AGIXresids = xts(resid(AGIXfit_weeks), order.by=as.Date(names(resid(AGIXfit_weeks))))

AGIXfit_month = lm(AGIX~ETH, data=month_annrets)
summary(AGIXfit_month)
ggplot(month_annrets,aes(y=AGIX, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
month_annrets2 = data.frame(date=names(resid(AGIXfit_month)))
month_annrets2$AGIXresids = resid(AGIXfit_month)
```

Next is the SingularityDAO token (SDAO):

```{r sdaoregs}
SDAOfit_daily = lm(SDAO~ETH, data=daily_annrets)
summary(SDAOfit_daily)
ggplot(daily_annrets,aes(y=SDAO, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
daily_annrets$SDAOresid = xts(resid(SDAOfit_daily), order.by=as.Date(names(resid(SDAOfit_daily))))

SDAOfit_weeks = lm(SDAO~ETH, data=weeks_annrets)
summary(SDAOfit_weeks)
ggplot(weeks_annrets,aes(y=SDAO, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
weeks_annrets$SDAOresids = xts(resid(SDAOfit_weeks), order.by=as.Date(names(resid(SDAOfit_weeks))))

SDAOfit_month = lm(SDAO~ETH, data=month_annrets)
summary(SDAOfit_month)
ggplot(month_annrets,aes(y=SDAO, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
month_annrets3 = data.frame(date=names(resid(SDAOfit_month)))
month_annrets3$SDAOresids = resid(SDAOfit_month)
month_annrets2 = merge(month_annrets2, month_annrets3, all.x=TRUE)
```

Then the NuNet token (NTX):

```{r ntxregs}
NTXfit_daily = lm(NTX~ETH, data=daily_annrets)
summary(NTXfit_daily)
ggplot(daily_annrets,aes(y=NTX, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
daily_annrets$NTXresid = xts(resid(NTXfit_daily), order.by=as.Date(names(resid(NTXfit_daily))))

NTXfit_weeks = lm(NTX~ETH, data=weeks_annrets)
summary(NTXfit_weeks)
ggplot(weeks_annrets,aes(y=NTX, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
weeks_annrets$NTXresids = xts(resid(NTXfit_weeks), order.by=as.Date(names(resid(NTXfit_weeks))))

NTXfit_month = lm(NTX~ETH, data=month_annrets)
summary(NTXfit_month)
ggplot(month_annrets,aes(y=NTX, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
month_annrets3 = data.frame(date=names(resid(NTXfit_month)))
month_annrets3$NTXresids = resid(NTXfit_month)
month_annrets2 = merge(month_annrets2, month_annrets3, all.x=TRUE)
```

Next is the Rejuve token (RJV):

```{r rjvregs}
RJVfit_daily = lm(RJV~ETH, data=daily_annrets)
summary(RJVfit_daily)
ggplot(daily_annrets,aes(y=RJV, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
daily_annrets$RJVresid = xts(resid(RJVfit_daily), order.by=as.Date(names(resid(RJVfit_daily))))

RJVfit_weeks = lm(RJV~ETH, data=weeks_annrets)
summary(RJVfit_weeks)
ggplot(weeks_annrets,aes(y=RJV, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
weeks_annrets$RJVresids = xts(resid(RJVfit_weeks), order.by=as.Date(names(resid(RJVfit_weeks))))

RJVfit_month = lm(RJV~ETH, data=month_annrets)
summary(RJVfit_month)
ggplot(month_annrets,aes(y=RJV, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
month_annrets3 = data.frame(date=names(resid(RJVfit_month)))
month_annrets3$RJVresids = resid(RJVfit_month)
month_annrets2 = merge(month_annrets2, month_annrets3, all.x=TRUE)
```

Then the HyperCycle token (HYPC):

```{r hypcregs}
HYPCfit_daily = lm(HYPC~ETH, data=daily_annrets)
summary(HYPCfit_daily)
ggplot(daily_annrets,aes(y=HYPC, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
daily_annrets$HYPCresid = xts(resid(HYPCfit_daily), order.by=as.Date(names(resid(HYPCfit_daily))))

HYPCfit_weeks = lm(HYPC~ETH, data=weeks_annrets)
summary(HYPCfit_weeks)
ggplot(weeks_annrets,aes(y=HYPC, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
weeks_annrets$HYPCresids = xts(resid(HYPCfit_weeks), order.by=as.Date(names(resid(HYPCfit_weeks))))

HYPCfit_month = lm(HYPC~ETH, data=month_annrets)
summary(HYPCfit_month)
ggplot(month_annrets,aes(y=HYPC, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
month_annrets3 = data.frame(date=names(resid(HYPCfit_month)))
month_annrets3$HYPCresids = resid(HYPCfit_month)
month_annrets2 = merge(month_annrets2, month_annrets3, all.x=TRUE)
```

Next is the Cogito token (CGV):

```{r cgvregs}
CGVfit_daily = lm(CGV~ETH, data=daily_annrets)
summary(CGVfit_daily)
ggplot(daily_annrets,aes(y=CGV, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
daily_annrets$CGVresid = xts(resid(CGVfit_daily), order.by=as.Date(names(resid(CGVfit_daily))))

CGVfit_weeks = lm(CGV~ETH, data=weeks_annrets)
summary(CGVfit_weeks)
ggplot(weeks_annrets,aes(y=CGV, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
weeks_annrets$CGVresids = xts(resid(CGVfit_weeks), order.by=as.Date(names(resid(CGVfit_weeks))))

CGVfit_month = lm(CGV~ETH, data=month_annrets)
summary(CGVfit_month)
ggplot(month_annrets,aes(y=CGV, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
month_annrets3 = data.frame(date=names(resid(CGVfit_month)))
month_annrets3$CGVresids = resid(CGVfit_month)
month_annrets2 = merge(month_annrets2, month_annrets3, all.x=TRUE)
```

Lastly is the Sophiaverse token (SOPH):

```{r sophregs}
SOPHfit_daily = lm(SOPH~ETH, data=daily_annrets)
summary(SOPHfit_daily)
ggplot(daily_annrets,aes(y=SOPH, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
daily_annrets$SOPHresid = xts(resid(SOPHfit_daily), order.by=as.Date(names(resid(SOPHfit_daily))))

SOPHfit_weeks = lm(SOPH~ETH, data=weeks_annrets)
summary(SOPHfit_weeks)
ggplot(weeks_annrets,aes(y=SOPH, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
weeks_annrets$SOPHresids = xts(resid(SOPHfit_weeks), order.by=as.Date(names(resid(SOPHfit_weeks))))

SOPHfit_month = lm(SOPH~ETH, data=month_annrets)
summary(SOPHfit_month)
ggplot(month_annrets,aes(y=SOPH, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
month_annrets3 = data.frame(date=names(resid(SOPHfit_month)))
month_annrets3$SOPHresids = resid(SOPHfit_month)
month_annrets2 = merge(month_annrets2, month_annrets3, all.x=TRUE)
```

Lastly, let's look at the ecosystem as a whole:

```{r snetregs}
SNETfit_daily = lm(SNET~ETH, data=daily_annrets)
summary(SNETfit_daily)
ggplot(daily_annrets,aes(y=SNET, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
daily_annrets$SNETresid = xts(resid(SNETfit_daily), order.by=as.Date(names(resid(SNETfit_daily))))

SNETfit_weeks = lm(SNET~ETH, data=weeks_annrets)
summary(SNETfit_weeks)
ggplot(weeks_annrets,aes(y=SNET, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
weeks_annrets$SNETresids = xts(resid(SNETfit_weeks), order.by=as.Date(names(resid(SNETfit_weeks))))

SNETfit_month = lm(SNET~ETH, data=month_annrets)
summary(SNETfit_month)
ggplot(month_annrets,aes(y=SNET, x=ETH))+
  geom_point()+
  geom_smooth(method="lm")
month_annrets3 = data.frame(date=names(resid(SNETfit_month)))
month_annrets3$SNETresids = resid(SNETfit_month)
month_annrets2 = merge(month_annrets2, month_annrets3, all.x=TRUE)
```

### Residual Correlations

Now that we have the residual series for each of the coins/tokens, let's look at the correlations between them. These represent the correlations of the asset returns after removing the effects that are explained by their relationship with Ethereum.

```{r dailyresidcors}
cor(daily_annrets[,10:17], use="pairwise.complete.obs") |> round(2)
```

```{r weeksresidcors}
cor(weeks_annrets[,10:17], use="pairwise.complete.obs") |> round(2)
```

```{r monthresidcors}
cor(month_annrets2[,-1], use="pairwise.complete.obs") |> round(2)
```

